<<<<<<< Updated upstream
---
title: "992 Proposal"
author: "Group 2"
output: html_document
---

#0. Read in the Data
=======
<<<<<<< Updated upstream
@@ -8,12 +8,57 @@ output: html_document
>>>>>>> Stashed changes
You may just need to run it once at the beginning of your work; after that, you'd better keep them as comments to save running time for `knitr`.
=======
---
<<<<<<< Updated upstream
title: "992 Proposal"
author: "Group 2"
output: html_document
=======
title: "992 proposal"
author: "Rong Ma"
date: "Sep 2, 2015"
output: pdf_document
>>>>>>> Stashed changes
---

#0. Read in the Data
You may need to run it once at the beginning of your work; after that, you'd better keep them as comments to save running time for `knitr`.
>>>>>>> Stashed changes

```{r}
load("~/Dropbox/STAT992/DataSource/Dat.RData")
load("~/Dropbox/STAT992/DataSource/Et.RData")
```

 
#1. Referral Network Clustering

```{r}
library(data.table)
library(igraph)
setkey(Et, V1) #setkey for Et
head(Et)
setkey(Dat, NPI) #setkey for Dat
head(Dat)

pie(-sort(-(table(Dat$"Provider Type"))))
providertype.top15=names(-sort(-table(Dat$`Provider Type`))[1:15])## almost 75% of Dat, the rest 25% is defined as others
Dat$`Provider Type`[which(!(Dat$`Provider Type` %in% providertype.top15))]="Others"
pie(-sort(-(table(Dat$"Provider Type"))))


tmp.link = Et[unique(Dat$NPI)] #link two data sets
tmp.link = tmp.link[complete.cases(tmp.link)] #only keep the complete cases
referral.matrix = as.matrix(tmp.link)[,1:2]
referral.undirected.graph = graph.edgelist(referral.matrix,directed=F)
referral.undirected.graph = simplify(referral.undirected.graph) #simplify the graph
core.referral.graph = graph.coreness(referral.undirected.graph) #get core
hist(core.referral.graph)
sum(core.referral.graph > 20)
referral.graph.all = induced.subgraph(graph=referral.undirected.graph,vids=V(referral.undirected.graph)[core.referral.graph>20])

#plot(referral.graph.all, vertex.label=NA, main = "Overall Network Graph") #Loooooong time to draw. Maybe we only focus on Wisconsin. In the following, to save your time, I "#" all the command lines and add the output.
#clust.referral.all = clusters(referral.graph.all) #clustering
#clust.referral.all$csize  #seems all connected
#[1] 140366
#clust.eigen.referral.all = cluster_leading_eigen(referral.graph.all)
#table(clust.eigen.referral.all$membership)
#    1     2     3     4     5     6     7     8     9    10 
#91579 16945  9327  3249   488 16503   704  1321    50   200 
#This seems a good clustering. To call the membership index you need to use the following command
#clust.eigen.referral.all$membership
```

Now we try the same thing on Wisconsin, so at least we have a graph on the network.

<<<<<<< Updated upstream
=======
=======
Now we try the same thing on Madison, so at least we have a graph on the network.
>>>>>>> Stashed changes
>>>>>>> Stashed changes
```{r}
wisc.referral = Dat[`NPPES Provider State`== "WI"]
tmp.link.wisc = Et[unique(wisc.referral$NPI)] #link two data sets
tmp.link.wisc = tmp.link.wisc[complete.cases(tmp.link.wisc)] #only keep the complete cases
referral.matrix.wisc = as.matrix(tmp.link.wisc)[,1:2]
referral.undirected.graph.wisc = graph.edgelist(referral.matrix.wisc,directed=F)
referral.undirected.graph.wisc = simplify(referral.undirected.graph.wisc) #simplify the graph
core.referral.graph.wisc = graph.coreness(referral.undirected.graph.wisc) #get core
hist(core.referral.graph.wisc)
sum(core.referral.graph.wisc > 20)
referral.graph.wisc = induced.subgraph(graph=referral.undirected.graph.wisc,vids=V(referral.undirected.graph.wisc)[core.referral.graph.wisc>20])
plot(referral.graph.wisc, vertex.label=NA, main = "Wisconsin Network Graph")
clust.referral.wisc = clusters(referral.graph.wisc) 
clust.referral.wisc$csize
clust.eigen.referral.wisc = cluster_leading_eigen(referral.graph.wisc)
table(clust.eigen.referral.wisc$membership)
third.cluster.wisc = induced.subgraph(graph=referral.undirected.graph.wisc,vids=(clust.eigen.referral.wisc$membership==3))
plot(third.cluster.wisc,vertex.label=NA,main = "Graph of 3rd cluster within WI")
<<<<<<< Updated upstream
```
=======
>>>>>>> Stashed changes

```
<<<<<<< Updated upstream

#2. plot with money and provider type,reason
```{r}
features = colnames(Dat)[c(3,7,12:14)]
print(features)

wisc.ids=V(referral.undirected.graph.wisc)$name
wisc.cities = wisc.referral[wisc.ids, mult = "first"]$`NPPES Provider City`
-sort(-table(wisc.cities))[1:10] #top 10 cities
mean(is.na(wisc.cities))
g=referral.undirected.graph.wisc
g = set.vertex.attribute(g, name = "city", index=V(g),value = wisc.cities)
madgraph = induced.subgraph(graph = g,vids = which(V(g)$city == "MADISON")) #subgraph for Madison
summary(madgraph)

madgraph.core = graph.coreness(madgraph) #get core
sum(madgraph.core)
madgraph.corereduce = induced.subgraph(graph=madgraph,vids=V(madgraph)[madgraph.core>10])#select core>10
sum(graph.coreness(madgraph.corereduce))

ids = V(madgraph.corereduce)$name
tmp =wisc.referral[ids, mult = "last"]
atbs = tmp[,features, with = F]  # Thank you google for helping to find "with"
mean(complete.cases(atbs))
atbs = as.matrix(atbs)
for(i in 1:ncol(atbs)){
madgraph.corereduce = set.vertex.attribute(madgraph.corereduce, name = colnames(atbs)[i], index=V(madgraph.corereduce),value =  atbs[,i])
}#add features to madgraph

locs = layout.auto(madgraph.corereduce)
summary(madgraph.corereduce)
V(madgraph.corereduce)$size <- (as.numeric(V(madgraph.corereduce)$`Total Medicare Payment Amount`))^(1/6)#set vertex size proportional to Total Medicare Payment Amount
plot(madgraph.corereduce, vertex.label = NA, vertex.color = as.factor(V(madgraph.corereduce)$"Provider Type"), layout = locs,main="Madison(Core>10)")#color the vertex according to Provider Type
legend('bottomleft',legend = unique(as.factor(V(madgraph.corereduce)$"Provider Type")),col=1:16,pch=16,cex = 0.4)
```


```{r}
str(Et$V2)

wisc.referral = Dat[`NPPES Provider State`== "WI"]
tmp.link.wisc = Et[unique(wisc.referral$NPI)] #link two data sets
tmp.link.wisc.forplot=tmp.link.wisc[which(tmp.link.wisc$V2 %in% wisc.referral$NPI)]
tmp.link.wisc.forplot = tmp.link.wisc.forplot[complete.cases(tmp.link.wisc.forplot)] #only keep the complete cases
referral.matrix.wisc.forplot = as.matrix(tmp.link.wisc.forplot)[,1:2]
referral.undirected.graph.wisc.forplot = graph.edgelist(referral.matrix.wisc.forplot,directed=F)
referral.undirected.graph.wisc.forplot = simplify(referral.undirected.graph.wisc.forplot) 
features = colnames(Dat)[c(3,7,12:14)]
wigraph=referral.undirected.graph.wisc.forplot


wigraph.core = graph.coreness(wigraph) #get core
sum(wigraph.core)
wigraph.corereduce = induced.subgraph(graph=wigraph,vids=V(wigraph)[wigraph.core>15])
sum(graph.coreness(wigraph.corereduce))


ids = V(wigraph.corereduce)$name
tmp =wisc.referral[ids, mult = "last"]
atbs = tmp[,features, with = F]  # Thank you google for helping to find "with" 1043240922
mean(complete.cases(atbs))
atbs = as.matrix(atbs)
for(i in 1:ncol(atbs)){
wigraph.corereduce = set.vertex.attribute(wigraph.corereduce, name = colnames(atbs)[i], index=V(wigraph.corereduce),value =  atbs[,i])
}
locs = layout.lgl(wigraph.corereduce)

V(wigraph.corereduce)$size <- (as.numeric(V(wigraph.corereduce)$`Total Medicare Payment Amount`))^(1/6)
plot(wigraph.corereduce, vertex.label = NA, vertex.color = as.factor(V(wigraph.corereduce)$"Provider Type"), layout = locs,main="Wisconsin(Core>15)")
legend('bottomleft',legend = unique(as.factor(V(wigraph.corereduce)$"Provider Type")),col=1:16,pch=16,cex = 0.4)
```

<<<<<<< Updated upstream
=======

Zipcode clusters
```{r}
library(zipcode)
data(zipcode);
zipcode = as.data.table(zipcode); 
setkey(zipcode, zip)

locs = zipcode[, c("longitude", "latitude"), with = F]
locs = locs[complete.cases(locs)]
sum(is.na(locs))
rownames(locs) = zips

library(deldir)
library(datautils) # this helps to fill in colors
library(maps)
library(grid)



dl = deldir(locs$long, locs$lat)  # find the tesselation
colss  = as.factor(sample(10,1:nrow(locs)))  # these are the colors of the zip codes.  ensure the elements line up with locs.

jpeg(filename = "tmp.jpeg",width = 230,height = 100, units = "in", res = 72)  # make it big so that the boarders are thin.  this is a hack!

plot.deldir(dl,wlines = "tess",wpoints = "none",lty = 0, fill = colss)

# whiteout anything outside the boarder. to  thanks stackoverflow.com/questions/16328438/how-can-i-color-the-ocean-blue-in-a-map-of-the-us
outline <- map("usa", plot=FALSE) # returns a list of x/y coords
xbox = par("usr")[1:2]; ybox = par("usr")[3:4]
# create the grid path in the current device
polypath(c(outline$x, NA, c(xbox, rev(xbox))),
         c(outline$y, NA, rep(ybox, each=2)),
         col="white", rule="evenodd")
dev.off()


getwd()

```

``` 
>>>>>>> Stashed changes
>>>>>>> Stashed changes
