---
title: "992 Proposal"
author: "Group 2"
output: html_document
---


#0. Read in the Data
You may need to run it once at the beginning of your work; after that, you'd better keep them as comments to save running time for `knitr`.


```{r}
load("~/Dropbox/STAT992/DataSource/Dat.RData")
load("~/Dropbox/STAT992/DataSource/Et.RData")
```
 
#1. Referral Network Clustering

```{r}
library(data.table)
library(igraph)
setkey(Et, V1) #setkey for Et
head(Et)
setkey(Dat, NPI) #setkey for Dat
head(Dat)

pie(-sort(-(table(Dat$"Provider Type"))))
providertype.top15=names(-sort(-table(Dat$`Provider Type`))[1:15])## almost 75% of Dat, the rest 25% is defined as others
Dat$`Provider Type`[which(!(Dat$`Provider Type` %in% providertype.top15))]="Others"
pie(-sort(-(table(Dat$"Provider Type"))))


tmp.link = Et[unique(Dat$NPI)] #link two data sets
tmp.link = tmp.link[complete.cases(tmp.link)] #only keep the complete cases
referral.matrix = as.matrix(tmp.link)[,1:2]
referral.undirected.graph = graph.edgelist(referral.matrix,directed=F)
referral.undirected.graph = simplify(referral.undirected.graph) #simplify the graph
core.referral.graph = graph.coreness(referral.undirected.graph) #get core
hist(core.referral.graph)
sum(core.referral.graph > 20)
referral.graph.all = induced.subgraph(graph=referral.undirected.graph,vids=V(referral.undirected.graph)[core.referral.graph>20])


#plot(referral.graph.all, vertex.label=NA, main = "Overall Network Graph") #Loooooong time to draw. Maybe we only focus on Wisconsin. In the following, to save your time, I "#" all the command lines and add the output.
#clust.referral.all = clusters(referral.graph.all) #clustering
#clust.referral.all$csize  #seems all connected
#[1] 140366
#clust.eigen.referral.all = cluster_leading_eigen(referral.graph.all)
#table(clust.eigen.referral.all$membership)
#    1     2     3     4     5     6     7     8     9    10 
#91579 16945  9327  3249   488 16503   704  1321    50   200 
#This seems a good clustering. To call the membership index you need to use the following command
#clust.eigen.referral.all$membership
#V(referral.graph.all)
```


Now we try the same thing on Wisconsin, so at least we have a graph on the network.

```{r}
wisc.referral = Dat[`NPPES Provider State`== "WI"]
tmp.link.wisc = Et[unique(wisc.referral$NPI)] #link two data sets
tmp.link.wisc = tmp.link.wisc[complete.cases(tmp.link.wisc)] #only keep the complete cases
referral.matrix.wisc = as.matrix(tmp.link.wisc)[,1:2]
referral.undirected.graph.wisc = graph.edgelist(referral.matrix.wisc,directed=F)
referral.undirected.graph.wisc = simplify(referral.undirected.graph.wisc) #simplify the graph
core.referral.graph.wisc = graph.coreness(referral.undirected.graph.wisc) #get core
hist(core.referral.graph.wisc)
sum(core.referral.graph.wisc > 20)
referral.graph.wisc = induced.subgraph(graph=referral.undirected.graph.wisc,vids=V(referral.undirected.graph.wisc)[core.referral.graph.wisc>20])
plot(referral.graph.wisc, vertex.label=NA, main = "Wisconsin Network Graph")
clust.referral.wisc = clusters(referral.graph.wisc) 
clust.referral.wisc$csize
clust.eigen.referral.wisc = cluster_leading_eigen(referral.graph.wisc)
table(clust.eigen.referral.wisc$membership)
third.cluster.wisc = induced.subgraph(graph=referral.undirected.graph.wisc,vids=(clust.eigen.referral.wisc$membership==3))
plot(third.cluster.wisc,vertex.label=NA,main = "Graph of 3rd cluster within WI")
```


#2. plot with money and provider type,reason

```{r}
library(colorspace)
Dat.type=Dat
pie(-sort(-(table(Dat$"Provider Type"))))
providertype.top15=names(-sort(-table(Dat$`Provider Type`))[1:15])## almost 75% of Dat, the rest 25% is defined as others
Dat.type$`Provider Type`[which(!(Dat$`Provider Type` %in% providertype.top15))]="Others"
pie(-sort(-(table(Dat.type$"Provider Type"))))

wisc.referral = Dat.type[`NPPES Provider State`== "WI"]
tmp.link.wisc = Et[unique(wisc.referral$NPI)] #link two data sets
tmp.link.wisc.forplot=tmp.link.wisc[which(tmp.link.wisc$V2 %in% wisc.referral$NPI)]
tmp.link.wisc.forplot = tmp.link.wisc.forplot[complete.cases(tmp.link.wisc.forplot)] #only keep the complete cases
referral.matrix.wisc.forplot = as.matrix(tmp.link.wisc.forplot)[,1:2]
referral.undirected.graph.wisc.forplot = graph.edgelist(referral.matrix.wisc.forplot,directed=F)
referral.undirected.graph.wisc.forplot = simplify(referral.undirected.graph.wisc.forplot) 
features = colnames(Dat.type)[c(3,7,12:14)]
wigraph=referral.undirected.graph.wisc.forplot


wigraph.core = graph.coreness(wigraph) #get core
sum(wigraph.core)
wigraph.corereduce = induced.subgraph(graph=wigraph,vids=V(wigraph)[wigraph.core>10])
sum(graph.coreness(wigraph.corereduce))


ids = V(wigraph.corereduce)$name
tmp =wisc.referral[ids, mult = "last"]
atbs = tmp[,features, with = F]  # Thank you google for helping to find "with" 1043240922
mean(complete.cases(atbs))
atbs = as.matrix(atbs)
for(i in 1:ncol(atbs)){
wigraph.corereduce = set.vertex.attribute(wigraph.corereduce, name = colnames(atbs)[i], index=V(wigraph.corereduce),value =  atbs[,i])
}

set.seed(1)
locs = layout.lgl(wigraph.corereduce)

V(wigraph.corereduce)$size <- (as.numeric(V(wigraph.corereduce)$`Total Medicare Payment Amount`))^(1/6)

#color

plot(wigraph.corereduce, vertex.label = NA,vertex.color = rainbow_hcl(10)[(as.factor(V(wigraph.corereduce)$"Provider Type"))], layout = locs,main="Wisconsin(Core>10)")

legend('topleft',legend = levels(as.factor(V(wigraph.corereduce)$'Provider Type')), col=rainbow_hcl(10), pch=16,cex = 0.5)
```



#3. Zipcode clusters

```{r}
library(zipcode)
library(dplyr)
library(ggplot2)
data(zipcode)
zipcode = as.data.table(zipcode) 
setkey(zipcode, zip)


clust.referral.all = clusters(referral.graph.all) #clustering
clust.eigen.referral.all = cluster_leading_eigen(referral.graph.all)
table(clust.eigen.referral.all$membership)
clust.eigen.referral.all$membership
which(as.numeric(names(V(referral.graph.all))) %in% zipToNPI$NPI)
clusterIndex = data.frame(NPI = names(V(referral.graph.all)), index = clust.eigen.referral.all$membership)

# The following code repeat the cluster using Zipcode instead of NPI:
zipToNPI = data.frame(zipcode = Dat$`NPPES Provider Zip Code`, NPI = Dat$NPI)
clusterIndex = merge(zipToNPI, clusterIndex, by = "NPI")

head(clusterIndex)


colnames(clusterIndex)[2] = "zip"
colnames(clusterIndex)[3] = "cluster"
zipdata = na.omit(merge(clusterIndex, zipcode, by = "zip"))
head(zipdata)
zipdata$cluster = as.factor(zipdata$cluster)
p = ggplot(data = zipdata, aes(x = longitude, y = latitude))
p + geom_point(aes(colour = cluster)) + xlim(-175, -50) 
  #scale_color_brewer(type = "qual", palette = 3) + 
```


#4.  Explore payment and build regression model within each cluster
 
```{r}
library(grDevices)
library(Matrix)
library(rARPACK)
library(plyr)
suppressPackageStartupMessages(library(dplyr))
library(ggplot2)
library(grid)
library(data.table)
library(igraph)

```


### Now we foucs on Wisconsin

```{r,echo=FALSE}
wisc.referral = Dat[`NPPES Provider State`== "WI"]
tmp.link.wisc = Et[unique(wisc.referral$NPI)] #link two data sets
tmp.link.wisc = tmp.link.wisc[complete.cases(tmp.link.wisc)] 
tmp.link.wisc<-tmp.link.wisc[which(tmp.link.wisc$V2 %in% wisc.referral$NPI)]  
# only keep the vertice in Wisconsin and individual
referral.matrix.wisc= as.matrix(tmp.link.wisc)[,1:2]
referral.undirected.graph.wisc= graph.edgelist(referral.matrix.wisc,directed=F)
referral.undirected.graph.wisc= simplify(referral.undirected.graph.wisc) #simplify the graph
```

###  Try some regression for WI

```{r,echo=FALSE}
deg.graph.wisc<-degree(referral.undirected.graph.wisc)
hist(deg.graph.wisc,col="lightblue",xlim=c(0, 200), xlab="Vertex Degree", ylab="Frequency", main="",breaks=150)   #  The degree distribution for the network,long tail
dis.graph.wisc<-degree.distribution(referral.undirected.graph.wisc)
dd<- 1:max(deg.graph.wisc)-1
ind <- (dis.graph.wisc!= 0)
plot(dd[ind], dis.graph.wisc[ind],log="xy",col="blue",xlab=c("Log-Degree"),ylab=c("Log-Intensity"), main="Log-Log Degree Distribution")      #   log–log scale Degree distribution  shows a fairly linear decay in the log-frequency as a function of log-degree

knn.deg.graph.wisc<- graph.knn(referral.undirected.graph.wisc,V(referral.undirected.graph.wisc))$knn     # Calculate the average nearest neighbor degree of the given vertices 
plot(deg.graph.wisc,knn.deg.graph.wisc, log="xy",col="goldenrod", xlab=c("Log Vertex Degree"), ylab=c("Log Average Neighbor Degree"))   # there is a tendency for vertices of higher degrees to link with vertices of relatively lower degrees, vertices of lower degree tend to link with vertices of both lower and higher degrees.


referral.wisc.data<-wisc.referral[V(referral.undirected.graph.wisc)]
deg.graph.wisc<-degree(referral.undirected.graph.wisc)
payment.wisc<-referral.wisc.data$`Total Medicare Payment Amount`
number.beneficiaries.wisc<-referral.wisc.data$`Number of Unique Beneficiaries`
number.service.wisc<-referral.wisc.data$`Number of Services`
average.age.wisc<-referral.wisc.data$`Average Age of Beneficiaries`
id.max.pay<-which(referral.wisc.data$`Total Medicare Payment Amount`==max(payment.wisc))
referral.wisc.data[id.max.pay] # the max payment is the type Ophthalmology  
plot(deg.graph.wisc[-1845],payment.wisc[-1845]) # plot degree vs. payment
plot(deg.graph.wisc,average.age.wisc)  # plot degree vs. age
plot(log(deg.graph.wisc),log(payment.wisc)) # plot degree vs. payment by log thansformation
fit1<-lm(payment.wisc~deg.graph.wisc)
summary(fit1)    # not significant 
```

The degree distribution for the network is long tail. And log–log scale Degree distribution  shows a fairly linear decay in the log-frequency as a function of log-degree. There is a tendency for vertices of higher degrees to link with vertices of relatively lower degrees, vertices of lower degree tend to link with vertices of both lower and higher degrees. The highest payment is the type Ophthalmology. The linear relationship for degree vs. payment is  not significant .   



```{r,echo=FALSE}
core.referral.graph.wisc = graph.coreness(referral.undirected.graph.wisc) 
#hist(core.referral.graph.wisc)
sum(core.referral.graph.wisc > 10)
referral.graph.wisc = induced.subgraph(graph=referral.undirected.graph.wisc,vids=V(referral.undirected.graph.wisc)[core.referral.graph.wisc>10])
set.seed(1)
locs = layout.lgl(referral.graph.wisc)
#plot(referral.graph.wisc,vertex.size=6,layout=locs,edge.arrow.size=0.05,vertex.label=NA, main = "Wisconsin Network Graph")
```



```{r,echo=FALSE}
features = colnames(Dat)[c(7,10,11,14)]
features
ids = V(referral.graph.wisc)$name
tmp = Dat[ids, mult = "last"]
atbs = tmp[,features, with = F]  
mean(complete.cases(atbs))

atbs = as.matrix(atbs)
for(i in 1:ncol(atbs)){
referral.graph.wisc= set.vertex.attribute(referral.graph.wisc, name = colnames(atbs)[i], index=V(referral.graph.wisc),value =  atbs[,i])
}
summary(referral.graph.wisc)
V(referral.graph.wisc)$size<-(as.numeric(V(referral.graph.wisc)$"Total Medicare Payment Amount"))^(1/6)

#plot(referral.graph.wisc, vertex.label = NA,vertex.color = as.factor(V(referral.graph.wisc)$"Provider Type"),layout = locs,edge.arrow.size=0.05,main="different colors for Provider Type")
```


###  use walktrap to detect community

```{r,echo=FALSE}
x<-par(bg="black")                    
referral.graph.wisc.com = walktrap.community(referral.graph.wisc, steps = 10)

V(referral.graph.wisc)$sg=referral.graph.wisc.com$membership
V(referral.graph.wisc)$color =rainbow(max(V(referral.graph.wisc)$sg),alpha=0.8)[V(referral.graph.wisc)$sg]

plot(referral.graph.wisc,layout=locs,vertex.size=1,vertex.color=V(referral.graph.wisc)$color,edge.width=0.5,edge.arrow.size=0.08,edge.color =rgb(1,1,1,0.4),vertex.frame.color=NA,margin= rep(0,4),vertex.label=NA)

```


### spectral cluster

```{r,echo=FALSE}
x<-par(bg="white")     
spectralClustering = function(g, k){
  A = get.adjacency(g)
  D = Diagonal(n = nrow(A), 1/sqrt(degree(g) + mean(degree(g))))
  L = D%*%A%*%D
  X = eigs(L,k)$vec
  X = t(apply(X, 1, function(x) return(x/sqrt(sum(x^2)))))
  set.seed(1)
  return(kmeans(X, k, nstart = 20))
  }   # function for spectral cluster algorithm
spec = spectralClustering(referral.graph.wisc, 25)  # to find 25 clusters
sort(table(spec$cluster))
referral.graph.wisc.npi<-V(referral.graph.wisc)$"name"

one.cluster.wisc<-induced.subgraph(graph=referral.graph.wisc,vids=(spec$cluster==13))
plot(one.cluster.wisc,vertex.label=NA,main = "Graph of one cluster within WI")   # for example, plot a cluster
```

### plot for spectral cluster

```{r,echo=FALSE}
x<-par(bg="black")                  
V(referral.graph.wisc)$sg.spec=spec$cluster
V(referral.graph.wisc)$color.spec =rainbow(max(V(referral.graph.wisc)$sg.spec),alpha=0.8)[V(referral.graph.wisc)$sg.spec]

plot(referral.graph.wisc,layout=locs,vertex.size=1,vertex.color=V(referral.graph.wisc)$color.spec,edge.width=0.5,edge.arrow.size=0.08,edge.color =rgb(1,1,1,0.4),vertex.frame.color=NA,margin= rep(0,4),vertex.label=NA)
x<-par(bg="white")  
 
```

### Take each cluster as a unit of observation, and obtain summary measures of the networks INSIDE each of those clusters. Try to find some relationship.

```{r,echo=FALSE}

#get a new data.frame including cluster class
average.payment<-as.numeric(V(referral.graph.wisc)$"Total Medicare Payment Amount")/as.numeric(V(referral.graph.wisc)$"Number of Services")

frame.referral.graph.wisc<-data.frame(referral.graph.wisc.npi,as.factor(spec$cluster),as.numeric(V(referral.graph.wisc)$"Total Medicare Payment Amount"),degree(referral.graph.wisc),average.payment)

colnames(frame.referral.graph.wisc)<-c("npi","class","payment","degree","average.payment")

summary.frame.referral.graph.wisc<-
  frame.referral.graph.wisc %>%
  group_by(class) %>%      
  summarize(mean_degree = mean(degree),mean_payment = mean(payment),mean_ave_pay=mean(average.payment)) 
head(summary.frame.referral.graph.wisc)

```

This is the summary data.frame for each cluster

regression for mean payment and  mean degree in each cluster

```{r,echo=FALSE}
plot(summary.frame.referral.graph.wisc[,-1])
fit<-lm(mean_payment~mean_degree,summary.frame.referral.graph.wisc)
summary(fit)     

```

 The positive liner relationship for mean payment and mean degree in each cluster is significant!


#5. Provider Type

```{r Zaiwei}
tmp.link = Et[unique(Dat$NPI)] #link two data sets
tmp.link = tmp.link[complete.cases(tmp.link)] #only keep the complete cases
tmp.link = tmp.link[which(tmp.link$V2 %in% Dat$`NPI`)]
referral.matrix = as.matrix(tmp.link)[,1:2]
referral.undirected.graph = graph.edgelist(referral.matrix,directed=F)
referral.undirected.graph = simplify(referral.undirected.graph) #simplify the graph
features = colnames(Dat)[7]
ids = V(referral.undirected.graph)$name
tmp = Dat[ids, mult = "last"]
atbs = tmp[,features, with = F]
mean(complete.cases(atbs))
atbs = as.matrix(atbs)
for(i in 1:ncol(atbs)){
  referral.undirected.graph = set.vertex.attribute(referral.undirected.graph, name = colnames(atbs)[i],
                                                   index=V(referral.undirected.graph), value =  atbs[,i])
}

table(V(referral.undirected.graph)$`Provider Type`)
Type.names <- sort(unique(V(referral.undirected.graph)$`Provider Type`))
Type.nums <- V(referral.undirected.graph)$`Provider Type` %>% as.factor() %>% as.numeric()

Type.c <- contract.vertices(referral.undirected.graph, Type.nums)
E(Type.c)$weight <- 1  # It takes a looong time to run. 
Type.c <- simplify(Type.c)

Type.size <- as.vector(table(V(referral.undirected.graph)$`Provider Type`))
plot(Type.c, vertex.size=1/50*sqrt(Type.size),
     vertex.label=Type.names, vertex.color=V(Type.c),
     edge.width=sqrt(E(Type.c)$weight), vertex.label.dist=1, edge.arrow.size=0)

```