
---
title: "992 Proposal"
author: "Group 2"
output: html_document
---


```{r}
load("~/Dropbox/STAT992/DataSource/Dat.RData")
load("~/Dropbox/STAT992/DataSource/Et.RData")
```

```{r}
library(grDevices)
library(Matrix)
library(rARPACK)
library(plyr)
suppressPackageStartupMessages(library(dplyr))
library(ggplot2)
library(grid)
library(data.table)
library(igraph)
```



```{r}
setkey(Et, V1) #setkey for Et
setkey(Dat, NPI) #setkey for Dat
```

### Now we foucs on Wisconsin

```{r}
wisc.referral = Dat[`NPPES Provider State`== "WI"]
tmp.link.wisc = Et[unique(wisc.referral$NPI)] #link two data sets
tmp.link.wisc = tmp.link.wisc[complete.cases(tmp.link.wisc)] 
tmp.link.wisc<-tmp.link.wisc[which(tmp.link.wisc$V2 %in% wisc.referral$NPI)]  
# only keep the vertice in Wisconsin and individual
referral.matrix.wisc= as.matrix(tmp.link.wisc)[,1:2]
referral.undirected.graph.wisc= graph.edgelist(referral.matrix.wisc,directed=F)
referral.undirected.graph.wisc= simplify(referral.undirected.graph.wisc) #simplify the graph
```

###  Try some regression for WI

```{r}
deg.graph.wisc<-degree(referral.undirected.graph.wisc)
hist(deg.graph.wisc,col="lightblue",xlim=c(0, 200), xlab="Vertex Degree", ylab="Frequency", main="",breaks=150)   #  The degree distribution for the network,long tail
dis.graph.wisc<-degree.distribution(referral.undirected.graph.wisc)
dd<- 1:max(deg.graph.wisc)-1
ind <- (dis.graph.wisc!= 0)
plot(dd[ind], dis.graph.wisc[ind],log="xy",col="blue",xlab=c("Log-Degree"),ylab=c("Log-Intensity"), main="Log-Log Degree Distribution")      #   log–log scale Degree distribution  shows a fairly linear decay in the log-frequency as a function of log-degree

knn.deg.graph.wisc<- graph.knn(referral.undirected.graph.wisc,V(referral.undirected.graph.wisc))$knn     # Calculate the average nearest neighbor degree of the given vertices 
plot(deg.graph.wisc,knn.deg.graph.wisc, log="xy",col="goldenrod", xlab=c("Log Vertex Degree"), ylab=c("Log Average Neighbor Degree"))   # there is a tendency for vertices of higher degrees to link with vertices of relatively lower degrees, vertices of lower degree tend to link with vertices of both lower and higher degrees.


referral.wisc.data<-wisc.referral[V(referral.undirected.graph.wisc)]
deg.graph.wisc<-degree(referral.undirected.graph.wisc)
payment.wisc<-referral.wisc.data$`Total Medicare Payment Amount`
number.beneficiaries.wisc<-referral.wisc.data$`Number of Unique Beneficiaries`
number.service.wisc<-referral.wisc.data$`Number of Services`
average.age.wisc<-referral.wisc.data$`Average Age of Beneficiaries`
id.max.pay<-which(referral.wisc.data$`Total Medicare Payment Amount`==max(payment.wisc))
referral.wisc.data[id.max.pay] # the max payment is the type Ophthalmology  
plot(deg.graph.wisc[-1845],payment.wisc[-1845]) # plot degree vs. payment
plot(deg.graph.wisc,average.age.wisc)  # plot degree vs. age
plot(log(deg.graph.wisc),log(payment.wisc)) # plot degree vs. payment by log thansformation
fit1<-lm(payment.wisc~deg.graph.wisc)
summary(fit1)    # not significant 
```

### plot the network

```{r}
core.referral.graph.wisc = graph.coreness(referral.undirected.graph.wisc) #get core
hist(core.referral.graph.wisc)
sum(core.referral.graph.wisc)
referral.graph.wisc = induced.subgraph(graph=referral.undirected.graph.wisc,vids=V(referral.undirected.graph.wisc)[core.referral.graph.wisc>10])
sum(referral.graph.wisc )
plot(referral.graph.wisc,vertex.size=6,layout=layout.fruchterman.reingold,edge.arrow.size=0.05,vertex.label=NA, main = "Wisconsin Network Graph")
```

### colors for type and sizes for payment

```{r}
features = colnames(Dat)[c(7,10,11,14)]
features
ids = V(referral.graph.wisc)$name
tmp = Dat[ids, mult = "last"]
atbs = tmp[,features, with = F]  
mean(complete.cases(atbs))

atbs = as.matrix(atbs)
for(i in 1:ncol(atbs)){
referral.graph.wisc= set.vertex.attribute(referral.graph.wisc, name = colnames(atbs)[i], index=V(referral.graph.wisc),value =  atbs[,i])
}
summary(referral.graph.wisc)

locs = layout.fruchterman.reingold(referral.graph.wisc)
summary(referral.graph.wisc)
V(referral.graph.wisc)$size<-(as.numeric(V(referral.graph.wisc)$"Total Medicare Payment Amount"))^(1/6)

plot(referral.graph.wisc, vertex.label = NA,vertex.color = as.factor(V(referral.graph.wisc)$"Provider Type"),layout = locs,edge.arrow.size=0.05,main="different colors for Provider Type")
```


###  use walktrap to detect community

```{r}
x<-par(bg="black")                    
referral.graph.wisc.com = walktrap.community(referral.graph.wisc, steps = 10)

V(referral.graph.wisc)$sg=referral.graph.wisc.com$membership
V(referral.graph.wisc)$color =rainbow(max(V(referral.graph.wisc)$sg),alpha=0.8)[V(referral.graph.wisc)$sg]

plot(referral.graph.wisc,layout=layout.fruchterman.reingold,vertex.size=1,vertex.color=V(referral.graph.wisc)$color,edge.width=0.5,edge.arrow.size=0.08,edge.color =rgb(1,1,1,0.4),vertex.frame.color=NA,margin= rep(0,4),vertex.label=NA)

```


### spectral cluster

```{r}
x<-par(bg="white")     
spectralClustering = function(g, k){
  A = get.adjacency(g)
  D = Diagonal(n = nrow(A), 1/sqrt(degree(g) + mean(degree(g))))
  L = D%*%A%*%D
  X = eigs(L,k)$vec
  X = t(apply(X, 1, function(x) return(x/sqrt(sum(x^2)))))
  set.seed(1)
  return(kmeans(X, k, nstart = 20))
  }   # function for spectral cluster algorithm
spec = spectralClustering(referral.graph.wisc, 25)  # to find 25 clusters
sort(table(spec$cluster))
referral.graph.wisc.npi<-V(referral.graph.wisc)$"name"

third.cluster.wisc<-induced.subgraph(graph=referral.graph.wisc,vids=(spec$cluster==15))
plot(third.cluster.wisc,vertex.label=NA,main = "Graph of the 15th cluster within WI")   # for example, plot a cluster
```

### plot for spectral cluster

```{r}
x<-par(bg="black")                  
V(referral.graph.wisc)$sg.spec=spec$cluster
V(referral.graph.wisc)$color.spec =rainbow(max(V(referral.graph.wisc)$sg.spec),alpha=0.8)[V(referral.graph.wisc)$sg.spec]

plot(referral.graph.wisc,layout=layout.fruchterman.reingold,vertex.size=1,vertex.color=V(referral.graph.wisc)$color.spec,edge.width=0.5,edge.arrow.size=0.08,edge.color =rgb(1,1,1,0.4),vertex.frame.color=NA,margin= rep(0,4),vertex.label=NA)
x<-par(bg="white")  
 
```

### Take each cluster as a unit of observation, and obtain summary measures of the networks INSIDE each of those clusters. Try to find some relationship.

```{r}

#get a new data.frame including cluster class
average.payment<-as.numeric(V(referral.graph.wisc)$"Total Medicare Payment Amount")/as.numeric(V(referral.graph.wisc)$"Number of Services")

frame.referral.graph.wisc<-data.frame(referral.graph.wisc.npi,as.factor(spec$cluster),as.numeric(V(referral.graph.wisc)$"Total Medicare Payment Amount"),degree(referral.graph.wisc),average.payment)

colnames(frame.referral.graph.wisc)<-c("npi","class","payment","degree","average.payment")

summary.frame.referral.graph.wisc<-
  frame.referral.graph.wisc %>%
  group_by(class) %>%      
  summarize(mean_degree = mean(degree),mean_payment = mean(payment),mean_ave_pay=mean(average.payment)) 
head(summary.frame.referral.graph.wisc)

```

This is the summary data.frame for each cluster

regression for mean payment and  mean degree in each cluster

```{r}
plot(summary.frame.referral.graph.wisc[,-1])
fit<-lm(mean_payment~mean_degree,summary.frame.referral.graph.wisc)
summary(fit)     #  significant!

```

###  check the average payment for different types

```{r}
wisc.referral$`Total Medicare Payment Amount`<-as.numeric(wisc.referral$`Total Medicare Payment Amount`) 

type.pay<-
wisc.referral%>%
  group_by(`Provider Type`) %>%      
  summarize(mean_p = mean(`Total Medicare Payment Amount`))  %>%  
  arrange(desc(mean_p))          
head(type.pay)

```

next we can explore a way to control the type, since the payment has relationship with the type.
